---
title: "Assignment 4"
author: "PGIS/M/DTS/20/09"
date: "8/13/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



```{r}
library(dplyr)
library(lavaan)
```


```{r}
ds <- read.csv("./academicachievement.csv")
head(ds)
```
Now , we write the model, then fit the model using lavaan syntax
```{r}
model <- '
  # measurement model
    adj =~ motivation + harmony + stability
    risk =~ parentalpsy + ses + verbal
    achiv =~ read + arith + spell 
  # regressions
    adj ~ risk
    achiv ~ adj + risk
    
  #residual correlation
  motivation ~~ read
  parentalpsy ~~ verbal + arith
  stability ~~ spell
  arith ~~ harmony
  stability ~~ parentalpsy
'
```

```{r}
fit <- sem(model, data = ds)
```

```{r}
summary(fit,standardized = TRUE,  fit.measures=TRUE)
```
Model Test User Model and Model Test Baseline Model P values are less than 0.05 model seems not significant. But the CFI and TLI values are greater than 0.90 because of that we can assume that we have a good fit.  RMSEA value should be less than 0.05 but it is greater than 0.05. SRMR Value  is less than 0.05 and we can consider it as good value.

Latent variables  P values are (less than 0.05) significant. Regression relations ships are also significant( P values less than 0.05). 

However, we can note that following covariances and variances are not significant, since the p value is > 0.05  
 
stability ~~  parentalpsy 
harmony ~~ arith
stability ~~ spell
parentalpsy ~~ verbal

We remove the nonsignificant  covariances ,and refit the model.

```{r}
modificationIndices(fit, minimum.value = 10)
 
```

```{r}
model2 <- '
  # measurement model
    adj =~ motivation + harmony + stability
    risk =~ parentalpsy + ses + verbal
    achiv =~ read + arith + spell 
  # regressions
    adj ~ risk
    achiv ~ adj + risk
    
  #residual correlation
  motivation ~~ read
  parentalpsy ~~ arith
'
```



```{r}
fit2 <- sem(model2, data = ds)
summary(fit2,standardized = TRUE, fit.measures=TRUE)
```
The CFI and TLI values are greater than 0.90 becase of that we can assume that we have a good fit.  RMSEA value should be less than 0.05 but it is greater than 0.05. SRMR Value  is less han 0.05 and we can consider it as good value.

Latent variables  P values are (less than 0.05) significant. Regression relations ships are also siginificant( P values less than 0.05). we can note that  covariances and variances are also significant, since the p value is < 0.05 .
.

```{r}
coef(fit2)
```
Show result in a table,

```{r}
standardizedsolution(fit2, type ="std.all")
```
Model Diagnostics,

We check the mismatch between the actual and estimated covarince matices
```{r}
fitted(fit2)
```
we can also get the fitted correlation matrix as follows,
```{r}
inspect(fit2, what="cor.all")
```
now we get the actual correlations
```{r}
resid(fit2, "cor")
```
For comparison of the estimated and actual correlations, it is better to consider the residuals. Larger positive residual values indicate the model under predicts the correlation and larger negative residual values suggest the overprediction of correlation. Usually |residual > 0.1| values should be closely checked.

Note that the |residual > 0.1|for motvtn with arith. Hence the model significantly underpredict the association between motvtn with arith.

If model does not fit well, we can inspect the modification indices and their corresponding expected parameter changes.
```{r}
mi <- modificationindices(fit2)
subset(mi ,mi >4)
```

```{r}
anova(fit,fit2)
```

```{r}
library(semPlot)
semPaths(fit, "std", edge.label.cex = 0.9, curvePivot = TRUE, layout = "tree", fade = FALSE)
```
