---
title: "Tutorial1"
author: "PGIS/M/DTS/20/09"
date: "9/26/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(TSstudio)
data("USVSales", package = "TSstudio")
```

## Class ts (time series)

```{r}
class(USVSales)
head(USVSales)
```
Data set can be assign to variable rather than loading to env (usually loadas to env)
```{r}
USV_Sales <- TSstudio::USVSales
```

## In here class is data.frame
```{r}
data("iris", package = "datasets")
str(iris)
class(iris)
```

```{r}
summary(iris)
```

## Quering the data
### datafram row column  index way: df[row,column]
```{r}
iris[1:5,2]
```
### Specifying specific variable in df
### df.variablename[rows]
```{r}
iris$Sepal.Width[1:5]
```
### Row index and column name i df
### df[rows, "column name"]

```{r}
iris[1:5, "Sepal.Width"]
```
### Or we can use a function
```{r}
iris[1:5, which(colnames(iris) == "Sepal.Width")]
```
### Taking two columns with specific rows
```{r}
iris[,c(2,3)]
```
## Subset the dataframe (not dplyr)
```{r}
setosa_df_1 <- subset(x = iris, iris$Species =="setosa")
head(setosa_df_1)
```
### Subset the dataframe using filter
```{r}
setosa_df_2 <- iris[which(iris$Species=="setosa"),]
head(setosa_df_2)
```
```{r}
identical(setosa_df_1,setosa_df_2)
```




